A simulation model of DNA methylation data

### 2015-03-25 Rmarkdown/methsim.Rmd
Fix dodgy figure path

These same distributions for all the _EPISCOPE_, _Lister_, _Seisenberger_ and _Ziller_ samples are shown in Figures \ref{fig:EPISCOPE_pattern_freqs_by_pm_boxplots}, \ref{fig:Lister_pattern_freqs_by_pm_boxplots}, \ref{fig:Seisenberger_pattern_freqs_by_pm_boxplots} and  \ref{fig:Ziller_pattern_freqs_by_pm_boxplots} (__TODO: Are these other examples necessary?__).

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../figures/Ziller_pattern_freqs_by_pm_boxplots.pdf}
\caption{$w_{(i, \ldots, i + m - 1) | r_{(i, \ldots, i + m - 1)}}, i = 1, \ldots, 2^{m} = 8$, the distribution of the relative frequencies for all CpG 3-tuples in each region type, for the \emph{Ziller} dataset. Only CpGs with at least $5\times$ sequencing coverage are used. UMR = unmethylated region; LMR = lowly methylated region; PMR = partially methylated region; other = any other region.}
\label{fig:Ziller_pattern_freqs_by_pm_boxplots}
\end{figure}

From Figures \ref{fig:EPISCOPE_pattern_freqs_by_pm_boxplots}, \ref{fig:Lister_pattern_freqs_by_pm_boxplots}, \ref{fig:Seisenberger_pattern_freqs_by_pm_boxplots} and \ref{fig:Ziller_pattern_freqs_by_pm_boxplots} we see that, unsurprisingly, in UMRs that a single methylation pattern dominates, the completely unmethylated pattern. Outside of UMRs, we see that while there is generally a dominant methylation pattern at each m-tuple, there may be $2-4$ otheres that are observed at non-negligible frequencies. PMRs are the most heterogeneous and LMRs and other regions are quite similar.

>>>>

These same distributions for all the _EPISCOPE_, _Lister_, _Seisenberger_ and _Ziller_ samples are shown in Figures \ref{fig:EPISCOPE_pattern_freqs_by_pm_boxplots}, \ref{fig:Lister_pattern_freqs_by_pm_boxplots}, \ref{fig:Seisenberger_pattern_freqs_by_pm_boxplots} and  \ref{fig:Ziller_merged_pattern_freqs_by_pm_boxplots} (__TODO: Are these other examples necessary?__).

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../figures/Ziller_merged_pattern_freqs_by_pm_boxplots.pdf}
\caption{$w_{(i, \ldots, i + m - 1) | r_{(i, \ldots, i + m - 1)}}, i = 1, \ldots, 2^{m} = 8$, the distribution of the relative frequencies for all CpG 3-tuples in each region type, for the \emph{Ziller} dataset. Only CpGs with at least $5\times$ sequencing coverage are used. UMR = unmethylated region; LMR = lowly methylated region; PMR = partially methylated region; other = any other region.}
\label{fig:Ziller_merged_pattern_freqs_by_pm_boxplots}
\end{figure}

From Figures \ref{fig:EPISCOPE_pattern_freqs_by_pm_boxplots}, \ref{fig:Lister_pattern_freqs_by_pm_boxplots}, \ref{fig:Seisenberger_pattern_freqs_by_pm_boxplots} and \ref{fig:Ziller_merged_pattern_freqs_by_pm_boxplots} we see that, unsurprisingly, in UMRs that a single methylation pattern dominates, the completely unmethylated pattern. Outside of UMRs, we see that while there is generally a dominant methylation pattern at each m-tuple, there may be $2-4$ otheres that are observed at non-negligible frequencies. PMRs are the most heterogeneous and LMRs and other regions are quite similar.
